%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ahmed El-Dakhakhny} \\ \vspace{1pt}
    \small (+20) 01115972875 $|$ \href{mailto:ahmd.eldakhakhny@gmail.com}{\underline{ahmd.eldakhakhny@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/eldakhakhny/}{\underline{linkedin.com/in/eldakhakhny/}} $|$
    \href{https://github.com/xenonzx}{\underline{github}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Software Engineer}{January 2021 -- Present}{\href{https://www.linkedin.com/company/blink22/}{\underline{Blink22}}}{Alexandria, Egypt}
        \resumeItemListStart
            \resumeItem{Played a pivotal role in developing Cashbook, scaling it to 500K MAUs in just 6 months. achieving over 1M installs.} 
            \resumeItem{Empower product teams to make data-driven decisions by harnessing customer insights through integrated analytics tools and SDKs.}  
            \resumeItem{Implemented A/B testing and feature flags to accelerate experimentation, optimize user experience, and enable gradual rollouts.}  
            \resumeItem{Implemented engaging features like GST calculator, full text search support and payment reminders to increase MoM retention and reduce the CAC.}  
            \resumeItem{Expanded app reach through supporting localization in 10+ languages.}  
            \resumeItem{Effectively managed release cycles, ensuring timely delivery of features while optimizing product performance and user retention through proactive crash analysis.}
            \resumeItem{Refactored and redesigned application components for improved performance and readability , leading to a more maintainable codebase.}
            \resumeItem{Conducted thorough code reviews and upheld high standards of code quality, ensuring consistency and reliability across the codebase.}
            \resumeItem{Integrated leading payment providers into Jumia Pay's infrastructure to enhance market presence and accelerate expansion across Africa.}
        \resumeItemListEnd
      \: Projects: \href{https://play.google.com/store/apps/details?id=com.khatabook.cashbook}{\underline{Cashbook by Khatabook}}, \href{https://play.google.com/store/apps/details?id=com.cassbana.cashkateb&hl=en}{\underline{CashKateb}}, \href{https://pay.jumia.com.eg/}{\underline{JumiaPay}}, \href{https://www.softcomputer.com/products-services/laboratory/}{\underline{SoftLab}}, Dreamr.
    \resumeSubheading{Android Team Lead}{August 2020 -- November 2020}{Amaz Egypt}{Alexandria, Egypt}
        \resumeItemListStart
            \resumeItem{Led the architectural design of a critical project, delivering a clear architecture, ensuring cross-teams alignment, and effectively fulfilling key business requirements."}
           \resumeItem{Implemented CI/CD pipelines for the Android team, significantly streamlining the development process and accelerating deployment cycles.}
           \resumeItem{Established a code review process, enhancing code quality and fostering a culture of continuous improvement.}        
           \resumeItem{Architected and Implemented MVVMI, a refined variation of the MVVM architecture, to better separate business use cases from ViewModels, thereby improving testability and maintainability.}
            \resumeItem{Introduced pair programming  and promoted knowledge sharing.}
        \resumeItemListEnd
    \resumeSubheading{Co-Founder and Tech Lead}{January 2019 -- August 2020}{Hafezah}{Riyadh, Saudi Arabia}
        \resumeItemListStart 
            \resumeItem{Collaborated in Developing comprehensive business models and a strategic business plan}
            \resumeItem{Defined product vision and key features, leading to a clear  actionable roadmap.}
            \resumeItem{Collaborated closely with the UX Engineer to achieve rapid MVP delivery while maintaining high standards of user experience with minimal compromises.}
            \resumeItem{Developed a prototype Python backend using Flask, successfully demonstrating the feasibility of core functionalities and supporting project validation.}
            \resumeItem{Managed the feature backlog, prioritizing features to accelerate time-to-market for the MVP}
            \resumeItem{Prototyped the system by delivering a Java-based Android application and a Flask-based Python backend, effectively showcasing the project's feasibility.}
            \resumeItem{ Directed the design and implementation of a scalable Node.js backend with LoopBack 3 and co-led the development of a marketplace app with Flutter, delivering a seamless cross-platform solution for Android and iOS.}     
            \resumeItem{ Utilized Scrum and Kanban methodologies to set sprint objectives, lead sprint planning and retrospectives, and oversee the testing and acceptance of deliverables from the tech team.}
            \resumeItem{ Designed and led interview process}       
            \resumeItem{Led financial planning and decision-making, overseeing budgeting, forecasting, and cash flow management.}

      \resumeItemListEnd
    \resumeSubheading{Software Engineer}{February 2016 -- December 2018}{\href{https://www.linkedin.com/company/badrit/}{\underline{BadrIT}}}{Alexandria, Egypt}
        \resumeItemListStart
            \resumeItem{Spearheaded the development of the AR core for Graphmented, the first AR Data Visualization app on iOS using Swift and ARKit. Successfully delivered and published the app on the App Store. Graphmented was later acquired by Incorta.}
            \resumeItem{Co-led the implementation and delivery of the mission-critical Android client for the Daif platform, a crowd management system active during Hajj. Daif manages, schedules, and tracks 17,000 buses in real-time, impacting approximately 1.8 million pilgrims each year.}
            \resumeItem{Spearheaded the development of the iOS app for Qmotor, the leading car dealership in Qatar. Contributed to the app's growth, supporting over 200k monthly active users.}
            \resumeItem{Contributed to Badr's Knowledge Academy by conducting tech talks on advanced Android development topics, including Gradle build system and MVP pattern.}

        \resumeItemListEnd
        \: Projects:  Killim, \href{https://www.youtube.com/watch?v=83msDwB3iIw}{\underline{Graphmented}}, \href{https://qmotor.com/}{\underline{Qmotor}},  Katara, \href{https://www.linkedin.com/company/winfooz/}{\underline{Winfooz}}, Badr's Tayar Delivery system, Badr's HR App, \href{https://www.seeloz.com/solutions}{\underline{Seeloz's MixaWallet}}.
    \resumeSubheading{Software Engineer}{June 2015 -- November 2015}{LuxTech}{Alexandria, Egypt}
    \resumeSubheading{Software Engineer}{March 2015 -- June 2015}{Arab E-Mall}{Alexandria, Egypt}
    \resumeSubheading{Software Engineer}{December 2014 -- March 2015}{ElSarhaBIM}{Alexandria, Egypt}
    \resumeSubheading{Android Developer}{August 2014 -- September 2014}{\href{https://www.linkedin.com/company/hdbc/}{\underline{HDBC}}}{Alexandria, Egypt}
    \resumeSubheading{Android Developer}{August 2013 -- September 2013}{\href{https://www.linkedin.com/company/venta-apps-llc/}{\underline{VentaApps}}}{Alexandria, Egypt}
\resumeSubHeadingListEnd

      
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading{Pharos University in Alexandria (PUA)}{Alexandria, Egypt}{Bachelor of Science in Computer Engineering}{July 2009 -- July 2014}

 \vspace{10pt}  
 \textit{\small Dual Certiﬁcation Pharos University in Alexandria and KTH Royal Institute of Technology Sweden.}
 \item Major: Computer Engineering
 \item CGPA: 3.48/4.0.
\resumeSubHeadingListEnd


\section{Certifications}
    \resumeItemListStart 
        \resumeItem{Certiﬁcate of Completion - Software Project Management, Software Engineering Competence Center-SECC, October 2019}
        \resumeItem{Android Developer Nanodegree, Udacity, February 2017}
        \resumeItem{Big Data Specialist with IBM BigInsights V2, IBM, September 2015}
        \resumeItemListEnd
\section{Hackathons and Competitions}
    \resumeItemListStart 
        \resumeItem{\href{https://gulfbusiness.com/saudis-hajj-hackathon-enters-records-worlds-largest/}{\underline{Hajj Hackathon}} (2nd place), 2018}
        \resumeItem{Hack4Egypt, 2015}
        \resumeItem{Create48, 2015}
        \resumeItem{ACM Alexandria Competitive Programming Competition, 2013}
        \resumeItem{Startup Weekend Alexandria, 2012}
    \resumeItemListEnd


% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, JavaScript, TypeScript, Swift} \\
     \textbf{Mobile}{: Android, IOS, Flutter} \\
     \textbf{Web Frameworks \& tools}{: Spring, Spring-boot, React, Node.js, Material-UI} \\
     \textbf{Developer Tools}{: Android Studio, Git, Docker, CircleCI, Gradle, Google Cloud Platform, Amazon Web Services AWS, VS Code, Visual Studio, IntelliJ} \\
     \textbf{Libraries}{: Redux, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
